Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-10 paper/main.tex
Udpate
Updates

\subsection{Improving DAGs using CI Testing}

@@

\section{Conclusions}
Researchers often prefer to construct DAGs manually rather than using automated
algorithms due to practical challenges in applying automated methods. To assist
in the process, we developed an iterative structure learning method that
integrates manual construction with data-driven insights. This approach bridges
the gap between fully manually and fully automated methods by providing a
systematic way to construct DAGs while utilizing data.

>>>>

@@

\section{Conclusions}
\todo[inline]{Rewrite}
Researchers often prefer to construct DAGs manually rather than using automated
algorithms due to practical challenges in applying automated methods. To assist
in the process, we developed an iterative structure learning method that
integrates manual construction with data-driven insights. This approach bridges
the gap between fully manually and fully automated methods by providing a
systematic way to construct DAGs while utilizing data.
